True versus apparent shapes of astrophysical bow shocks

### 2017-09-12 papers/Paper1/sec-conclusions.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote
Improve Fig 8 on projection of quadrics
Now with 4 panels (incorporates what was in Fig 9 previously).  Use
better color scheme: a diverging set of 7 colors around
T=0 (black). Get rid of the varying line types and use varying
thickness instead. Additional panel showing R90' versus i.

\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

@@

Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
density follows a power law of $\cos\theta$. Altrough other models also may be used.

In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}

>>>>

%\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

@@

Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
density follows a power law of $\cos\theta$. Although other models also may be used.

In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
(ONC) due to the interaction of the photoevaporated wind from proplyds and the stellar wind of \thC{}.

### 2017-09-12 papers/Paper1/sec-conic.tex
Improve Fig 8 on projection of quadrics
Now with 4 panels (incorporates what was in Fig 9 previously).  Use
better color scheme: a diverging set of 7 colors around
T=0 (black). Get rid of the varying line types and use varying
thickness instead. Additional panel showing R90' versus i.

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.45\linewidth}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution.
    Variation with inclination of characteristic radii.}
  \label{fig:quadric-projection}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-vs-Rc}
  \caption{Diagnostic diagram for projected quadric parameters}
  \label{fig:projected-R90-vs-Rc}
\end{figure}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of projected quadric parameters}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}
Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)+x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

>>>>

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
    (c) & (d) \\
    \includegraphics{figs/projected-R90-vs-i}
    & \includegraphics{figs/projected-R90-vs-Rc}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination of characteristic radii. In panels
    (a)--(c), vertical rectangles show quartiles of \(|\sin i|\), which
    will be equally populated for an isotropic distribution of
    orientations. (a)~Projected radius of curvature, normalized by
    projected stand-off distance: \( \tilde{R}_c' = R'_c /
    R'_0\). (b)~Projected stand-off distance: \(R_0' / R_0\).
    (c)~Projected perpendicular radius, normalized by projected
    stand-off distance: \( \tilde{R}_{90}' = R'_{90} /
    R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\). }
  \label{fig:quadric-projection}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of projected quadric parameters}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}
Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)+x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}
